\documentclass[letterpaper,12pt]{letter}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{pdfsync}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Calibri}
\setmonofont{Inconsolata}
\setmainfont{Linux Libertine}
% To reduce the vertical space at the top:
\topmargin -3.3cm
\textheight 28cm
%\oddsidemargin 0.3cm
%\evensidemargin 0.3cm
%\textwidth 16.1cm 

\address{Sean C. Anderson\\Biological Sciences\\Simon Fraser University\\Burnaby, BC, V5A 1S6\\Canada\\sean@seananderson.ca}

\begin{document}
\begin{letter}{}
\pagestyle{empty}
\opening{Dear D. Holyoak} % eg Hello.

Please find enclosed a manuscript entitled ``Portfolio conservation of metapopulations under climate change'' that we wish to submit for possible publication as a Letter in Ecology Letters.

XX

We confirm that XX. All authors have approved the manuscript and agree with
its submission to Ecology Letters.

This work is timely given the large and expanding interest in XX, the unusual super-abundance of American lobster, and the largely unknown mechanisms driving XX. The results will be of broad interest to Ecology Letters readers due to XX. 

This work is entirely original; none of it has been previously published and is not under consideration elsewhere. This manuscript has been approved by all authors. No other recent work of ours deals with the topic presented in this paper. MEE Paper? Ecol Lett paper Yeakel?

We would like to suggest the following five independent referees, listed alphabetically:

Thank you for considering our manuscript for publication and we look forward to hearing from you.

\vspace{14mm}
\closing{Sincerely,\\
\fromname{Sean Anderson, Jonathan Moore, Michelle McClure, Nicholas Dulvy, Andrew Cooper}
}

\end{letter}
\end{document}

